%-------------------------
% Resume in Latex
% Author : Qian Bao
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

% TIPA is a system for processing phonetic symbols in latex. 
\usepackage{tipa}
% Heart of xelatex. In order to utilize ttf and ttc font.
\usepackage{fontspec}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
%------------------------
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%------------------------
%  CV STARTS HERE
%------------------------

\begin{document}

%---------HEADING--------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/houkensjtu}{\Large Qian Bao}} & Email : \href{mailto:houkensjtu@gmail.com}{houkensjtu@gmail.com}\\
   & Mobile : +1-610-704-4131 \\
\end{tabular*}


%-----------SKILLS-----------------
\section{Skills Summary}
  \resumeSubHeadingListStart

    \resumeSubItem{Thermal fluid analysis}
      { General knowledge in fluid dynamics, heat transfer and CFD. 5+ years experience in a next-generation mechanical product R\&D team. 
      \begin{itemize}
      \item Developed component level thermal fluid models (using Python, Fortran and opensource library (OpenFOAM)) to assist product design and accelerated development cycle. 
      \item Hands-on analysis skills in Ansys Mechanical / Fluent to facilitate and accelerate product prototyping.
      \item Hands-on experience on thermal and fluid tests of prototpye products. Wrote data acquisition code to collect / analyze experimental data to facilitate prototyping.      
      \end{itemize}}

    \resumeSubItem{Computer science related}
      {Self learned a broad range of undergraduate level computer science courses including but not limited to:
      \begin{itemize}
      \item Fundamental of machine learning (Coursera online course by Andrew Ng.)
      \item Principles of imperative computation (C) and object-oriented programming (Python)
      \item Data structure and algorithms (Java/Python)
      \end{itemize}
      }
    
    \resumeSubItem{Mechanical design}
      {General knowledge of mechanical system, manufacturing process and design process.
      \begin{itemize}
        \item 5+ years experience in 2D mechanical drawings, GD\&T design and 3D modeling. 
        \item 3+ years experience in Solidworks. CSWA certificated by Solidworks.
      \end{itemize}
      }


    \resumeSubHeadingListEnd

%-----EXPERIENCE----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {Sumitomo Cryogenics of America, Inc}{Allentown, PA}
    {Research Engineer, Project Leader}{Oct 2018 - Present}
    \resumeItemListStart
      \resumeItem{Development of pneumatic drive high capacity Gifford-McMahon cryocooler}
        {  \begin{itemize}
           \item {Leading a cross-functional team operating the R\&D of a next-generation cryocooler product. }
           \item {Facilitated the communication among design team, business stakeholders, global partners and headquarters.}
           \end{itemize}
        }
    \resumeItemListEnd

    \resumeSubheading
      {Sumitomo Heavy Industries, Ltd.}{Tokyo, Japan}
      {Research Engineer}{Apr 2013 - Sep 2018}
      \resumeItemListStart
        \resumeItem{Development of next generation 2K Gifford-McMahon cryocooler}
        {  
           \begin{itemize}
           \item{Carried out numerical analysis of cryocooler products and designed the key components (heat exchanger etc.) of a new, highly compact Gifford-McMahon cryocooler
           which can achieve 2K on its second stage. Also built customized measurement system (GPIB) to test the prototype unit.}
           \item{Based on this work, published 2 papers in international cryogenic conference and 1 journal paper in Japan. 
           The design result is recognized as the most compact 2K Gifford-McMahon cryocooler in the world.}
           \item {This project was supported by the National Institute of Information and Communications Technology (NICT), JAPAN.}
          \end{itemize}
        }
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  

%------EDUCATION---------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tohoku University}{Sendai, Japan}
      {Master of Engineering in Graduate School of Mechanical Engineering;  GPA: 3.7/4.0}{Oct. 2010 -- Mar. 2013}

      Thesis : Study of Heat Transfer and Fluid Flow of Bubbles in a microchannel; Advisor : Shigenao Maruyama

    \resumeSubheading
      {Shanghai Jiaotong University}{Shanghai, China}
      {Bachelor of Engineering in School of Mechanical Engineering;  GPA: 3.5/4.0}{Sep. 2006 -- Jun. 2010}

      Thesis : Mass flow distribution behavior of liquid nitrogen in a minichannel heat sink; Advisor : Peng Zhang

    \resumeSubheading
      {Shanghai Jiaotong University}{Shanghai, China}
      {Bachelor of Arts in School of Foreign Language;  Minor in Japanese language}{Sep. 2008 -- Jun. 2010}

  \resumeSubHeadingListEnd

%----------Language skill-------
\section{Language Certification}
\resumeSubHeadingListStart
  \resumeSubItem{Mandarin Chinese}{Mother tongue}
  \resumeSubItem{English}{Professional efficiency; TOEFL iBT 114/120; GRE V156 + Q170; TOEIC 965/990}
  \resumeSubItem{Japanese}{Professional efficiency; JLPT N1 176/180}
  \resumeSubItem{German}{Intermediate efficiency; CEFR B1}
\resumeSubHeadingListEnd


%----------Publications-------
\section{Publication}
1.Experimental Investigation of Compact 2 K GM Cryocoolers, Physics Procedia, Volume 67, Pages 428-433, ISSN 1875-3892,
https://doi.org/10.1016/j.phpro.2015.06.053., (25th International Cryogenic Engineering Conference and the International Cryogenic Materials Conference in 2014, ICEC 25–ICMC 2014, Netherland)

2.Development of a compact 2K GM cryocooler, Cryogenic engineering (Japanese), Vol.50 (2015) No.3 p. 125-131

3.Recent development status of compact 2 K GM cryocoolers,
IOP Conference Series: Materials Science and Engineering,
volume 101,
p.012136.
(Cryogenic Engineering Conference ,CEC 2015: Tucson, AZ, USA, June 28 - July 2, 2015)

4.Development status of a high cooling capacity single stage GM cryocooler,
Cryocooler 19,
pp. 291-297,
(International Conference of cryocoolers ,ICC19: San Diego, CA, USA, June 20-23, 2016)

5.Development of a pneumatic GM cryocooler with dual-displacer (Oral presentation, International workshop on cooling of HTS-Applications, IWC-HTS, Karlsruhe, Germany, September 13-15, 2017)

%----------Patent-------------
\section{Patent}
1. A. T. A. M de Waele, Mingyao Xu and Qian Bao. Method to achieve temperature lower than 2K in a Gifford-McMahon cryocooler. U.S. Patent 10,197,305. Filed Dec 21,2015. Issued Feb 5,2019.

2. Mingyao Xu and Qian Bao. Optimization of concentric heat exchanger for cryogenic refrigerator. U.S. Patent 9,841,212. Filed Apr 2,2015. Issued Dec 12,2017.

3. Mingyao Xu, Takaaki Morie and Qian Bao. A high-efficiency dual-cylinder design of Gifford-McMahon cryocooler. U.S. Patent 10,184,693. Filed Oct 20,2016. Issued Jan 22,2019.

\end{document}
