% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[12pt,A4]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{tipa}
% Heart of xelatex. In order to utilize ttf and ttc font.
\usepackage{fontspec}

% For english characters and numbers, Times New Roma seems to be perfect.
\setmainfont[ Path = fonts/,BoldFont = timesbd]{times}
\makeatletter
\newlength\tdima
\newcommand\tabright[1]{%
      \setlength\tdima{\linewidth}%
      \addtolength\tdima{\@totalleftmargin}%
      \addtolength\tdima{-\dimen\@curtab}%
      \makebox[\tdima][r]{#1}}
\makeatother

% \setlength{\textheight}{9.5in} % increase text height to fit on 1-page 

\usepackage[top=1in, bottom=1.5in, left=1.0in, right=1.4in]{geometry}
\renewcommand{\namefont}{\bfseries\LARGE}
\begin{document} 

\name{Qian Bao\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name      

\address{\textbf{PRESENT ADDRESS}\\Yato-cho 2chome 2-9 Room 510\\Nishitokyo-city,Tokyo\\Japan, Postcode: 188-0001}
\address{\textbf{CONTACT INFO} \\ Email: houkensjtu@gmail.com \\ Mobile: +81-090-9427-1113 \\  Phone: +81-042-468-4474}
                                  
\begin{resume}

\section{ABOUT ME}          
Hi! I am Bao /\textipa{baU}/. I' m currently working as a research engineer in Sumitomo Heavy Industries, Ltd. in Japan,
 my work focus on design and development of next-generation GM type cryocoolers. I earned my Bachelor and Master degree
 with a major in Mechanical Engineering. Besides my job, which is mainly concerned with Engineering fluid dynamics and heat transfer,
  I am particularly enamored with Linux, open-source software and electronic gadgets.


\section{EDUCATION}      
    \vspace{-0.1in}	    

   \begin{tabbing}
    \hspace{2.2in}\= \hspace{2.1in}\= \kill % set up two tab positions
    {\bf Tohoku University} \> \tabright{2010.7-2013.3}\\
    Department: Mechanical Systems and Design, Master of Engineering\\
    Thesis: Study of Fluid Flow and Heat Transfer Behavior of Bubbles in a microchannel\\
     \> \tabright{Advisor: Prof. S. Maruyama}\\
   \end{tabbing}\vspace{-38pt}      % suppress blank line after tabbing
    Selected courses:\\\vspace{-10pt}
    \begin{itemize}
      \item Theoretical Basics of Fluid Dynamics
      \item Computational Fluid Dynamics
      \item Thermal Science and Engineering
      \item Environmental Heat-Transfer Control
    \end{itemize}   
    \vspace{-0.1in}
    
    \begin{tabbing}
    \hspace{2.2in}\= \hspace{2.1in}\= \kill % set up two tab positions
    {\bf Shanghai Jiaotong University} \> \tabright{2006.9-2010.7} \\
    Department: School of Mechanical Engineering, Bachelor of Engineering\\
    Thesis: Mass flow distribution behavior of liquid nitrogen in a minichannel heat sink \\
    \> \tabright{Advisor: Prof. P. Zhang}\\
   \end{tabbing}\vspace{-40pt}      % suppress blank line after tabbing    
    Selected courses:\\\vspace{-10pt}
    \begin{itemize}
      \item Engineering Fluid Mechanics
      \item Computational Fluid and Heat Transfer
      \item Heat Transfer and Mass Transfer
      \item Engineering Thermodynamics
      \item Programming Abstractions
      \item Aerodynamics and Two-phase Flow
      \item Cryogenic Technology and Applications
    \end{itemize}
    
    \vspace{-0.1in}
    \begin{tabbing}
    \hspace{2.2in}\= \hspace{2.1in}\= \kill % set up two tab positions
    {\bf Shanghai Jiaotong University} \> \tabright{2008.9-2010.7} \\
    Department: School of Foreign Languages, Bachelor of Arts\\
    \end{tabbing}
    
\section{EMPLOYMENT}
    \vspace{-0.1in}	    
    \begin{tabbing}
    \hspace{2.2in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Sumitomo Heavy Industries, Ltd.} \>  \>2013.4-Present
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
   
     
\section{EXPERIENCE}
   \vspace{-0.1in}	
   \begin{tabbing}
   \hspace{2.0in}\= \hspace{2.0in}\= \kill % set up two tab positions
    {\bf Telefund Associate} \>Rensselaer Fund     \>Fall 1987-Present\\
                             \>Troy, NY
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Generated alumni and parent support to reduce tuition,          
    increase scholarship and financial aid funds; averaging 80          
    percent pledge rate. Top three percent associate.
   \begin{tabbing}
   \hspace{2.0in}\= \hspace{2.0in}\= \kill % set up two tab positions
    {\bf Team Programmer} \>Group W Cable, Westinghouse Corp \> ~~~~~~ Summer 1987\\
                          \>Mahway, NJ
   \end{tabbing}\vspace{-20pt}
    Liaison between accounting department and controller,          
    provided assistance with invoice liabilities after          
    divestiture of Group W Cable by Westinghouse.
   \begin{tabbing}%
   \hspace{2.0in}\= \hspace{2.0in}\= \kill % set up two tab positions          
   {\bf Sales Assistant}  \>AP Technical Sales Inc. \> Summers  1985-86\\
                          \>Palisades Park, NJ
   \end{tabbing}\vspace{-20pt}
    Duties included telemarketing, data entry, and invoicing.          
    Successfully converted catalog inquiries to sales          
    opportunities by telemarketing program.          


\section{COMPUTER SKILLS}          
    Extensive knowledge of hardware and software for IBM PC and          
    MTS. \\         
    Proficient programming skills in COBOL, WATFIV (FORTRAN), and          
    BASIC.          
 
 
\section{HONORS AND AWARDS}          
    Some honor... 

\end{resume}
\end{document}
