% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[12pt,A4]{res} 

% TIPA is a system for processing phonetic symbols in latex. 
\usepackage{tipa}

% Heart of xelatex. In order to utilize ttf and ttc font.
\usepackage{fontspec}

% For english characters and numbers, Times New Roma seems to be perfect.
\setmainfont[ Path = fonts/,BoldFont = timesbd]{times}

% A macro used to provide a right tab.
\makeatletter
\newlength\tdima
\newcommand\tabright[1]{%
      \setlength\tdima{\linewidth}%
      \addtolength\tdima{\@totalleftmargin}%
      \addtolength\tdima{-\dimen\@curtab}%
      \makebox[\tdima][r]{#1}}
\makeatother

% increase text height to fit on 1-page 
\setlength{\textheight}{9.5in} 

\usepackage[top=1in, bottom=1.5in, left=1.0in, right=1.4in]{geometry}

% To size up the display of Name region.
\renewcommand{\namefont}{\bfseries\LARGE}


\begin{document} 

% the \\[12pt] adds a blank line after name    
\name{Qian Bao\\[12pt]}  

\address{\textbf{PRESENT ADDRESS}\\ Postcode: 188-0001 \\Yato-cho 2chome 2-9 Room 510\\Nishitokyo-city,Tokyo\\Japan}
\address{\textbf{PERSONAL DATA} \\Date of birth: 1987.11.13 \\ Place of birth: Shanghai, China \\ Gender: Male \\Email:houkensjtu@gmail.com}
                                  
\begin{resume}

\section{ABOUT ME} 
Hi! I am Bao /\textipa{baU}/. I' m currently working as a research engineer at Sumitomo Heavy Industries, Ltd. in Japan.
 My work focus on design and development of next-generation GM type cryocoolers. Before that, I earned my Bachelor and Master degree
 with a major in Mechanical Engineering. Besides my job, I am particularly enamored with Linux, open-source software ,electronic gadgets and foreign language learning.

\section{EDUCATION}      
    \vspace{-0.1in}	    

   \begin{tabbing}
    \hspace{2.2in}\= \hspace{2.1in}\= \kill % set up two tab positions
    {\bf Tohoku University (In: Sendai, Japan)} \> \tabright{2010.7-2013.3}\\
    Department: Graduate School of Engineering, Master of Engineering\\
    Thesis: Study of Heat Transfer and Fluid Flow of Bubbles in a microchannel\\
     \> \tabright{Advisor: Prof. S. Maruyama}\\
   \end{tabbing}\vspace{-38pt}      % suppress blank line after tabbing
    Selected courses:\\\vspace{-10pt}
    \begin{itemize}
      \item Theoretical Basics of Fluid Dynamics
      \item Computational Fluid Dynamics
      \item Thermal Science and Engineering
      \item Environmental Heat-Transfer Control
    \end{itemize}   
    \vspace{-0.1in}
    
    \begin{tabbing}
    \hspace{2.2in}\= \hspace{2.1in}\= \kill % set up two tab positions
    {\bf Shanghai Jiaotong University (In: Shanghai, China)} \> \tabright{2006.9-2010.7} \\
    Department: School of Mechanical Engineering, Bachelor of Engineering\\
    Major: Thermal Energy and Power Engineering\\
    Thesis: Mass flow distribution behavior of liquid nitrogen in a minichannel heat sink \\
    \> \tabright{Advisor: Prof. P. Zhang}\\
   \end{tabbing}\vspace{-40pt}      % suppress blank line after tabbing    

    Selected courses:\\\vspace{-10pt}
    \begin{itemize}
      \item Engineering Fluid Mechanics
      \item Computational Fluid Dynamics and Heat Transfer
      \item Heat and Mass Transfer
      \item Engineering Thermodynamics
      \item Programming Abstractions
      \item Aerodynamics and Two-phase Flow
      \item Cryogenic Technology and Applications
    \end{itemize}
    
    \vspace{-0.1in}
    \begin{tabbing}
    \hspace{2.2in}\= \hspace{2.1in}\= \kill % set up two tab positions
    {\bf Shanghai Jiaotong University (In: Shanghai, China)} \> \tabright{2008.9-2010.7} \\
    Department: School of Foreign Languages, Bachelor of Arts \bf{(second degree)}\\
    Major: Japanese Language\\
    \end{tabbing}
    
\section{EMPLOYMENT}
    \vspace{-0.1in}	    
    \begin{tabbing}
    \hspace{2.2in}\= \hspace{2.1in}\= \kill % set up two tab positions
    {\bf Sumitomo Heavy Industries, Ltd. (In: Tokyo, Japan)} \> \tabright{2013.4-Present} \\
    Department: Technology Research Center, Research Engineer \\
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing

    Selected Project: “Development of a Compact Superconducting Single Photon
    Detector System for Photon-Quantum Information and Communication”, supported by
    the National Institute of Information and Communications Technology (NICT), JAPAN. \\
    \\
    Scope of work: Design, simulation and experimental test of next-generation GM (Gifford-McMahon) type cryocoolers.\\   
     
\section{LANGUAGE SKILLS}
Mandarin Chinese (mother tongue) \\
English (professional efficiency, TOEFL iBT 108) \\
Japanese (full professional efficiency, JLPT N2) \\
German (elementary)     

\section{COMPUTER SKILLS}          
Solid operation knowledge of Linux (long time hobbyist) \\
Programming language experienced: C, C++, Python, Fortran, Matlab \\
Basic operation knowledge: ANSYS Fluent, OpenFOAM, Gerris, CAD \\
Programming of measurement instruments over GPIB using VISA \\
Fundamental understanding of Computer Science (by self-learning) \\
And curiosity towards any unknown hardware / software !
 
\section{HONORS AND AWARDS}          
2010.7-2011.3 Japanese government (MONBUKAGAKUSHO:MEXT) scholarship for research students\\

\end{resume}
\end{document}
