%-------------------------
% Resume in Latex
% Author : Qian Bao
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

% TIPA is a system for processing phonetic symbols in latex. 
\usepackage{tipa}
% Heart of xelatex. In order to utilize ttf and ttc font.
\usepackage{fontspec}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
%------------------------
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%------------------------
%  CV STARTS HERE
%------------------------

\begin{document}

%---------HEADING--------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sourabhbajaj.com/}{\Large Qian Bao}} & Email : \href{mailto:houkensjtu@gmail.com}{houkensjtu@gmail.com}\\
  Address : 3273 W. Cedar Street, Allentown, 18104 PA & Mobile : +1-610-704-4131 \\
\end{tabular*}


%------EDUCATION---------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tohoku University}{Sendai, Japan}
      {Master of Engineering in Graduate School of Mechanical Engineering;  GPA: 3.7/4.0}{Oct. 2010 -- Mar. 2013}
      
      Thesis : Study of Heat Transfer and Fluid Flow of Bubbles in a microchannel; Advisor : Shigenao Maruyama

    \resumeSubheading
      {Shanghai Jiaotong University}{Shanghai, China}
      {Bachelor of Engineering in School of Mechanical Engineering;  GPA: 3.5/4.0}{Sep. 2006 -- Jun. 2010}
      
      Thesis : Mass flow distribution behavior of liquid nitrogen in a minichannel heat sink; Advisor : Peng Zhang
  \resumeSubHeadingListEnd


%-----EXPERIENCE----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {Sumitomo Cryogenics of America, Inc}{Allentown, PA}
    {Research Engineer}{Oct 2018 - Present}
    \resumeItemListStart
      \resumeItem{Development of pneumatic drive high capacity Gifford-McMahon cryocooler}
      {Leading the R\&D of a next-generation cryocooler product. Carried out numerical thermal/mechanical analysis of the key components
      and proposed the prototyping strategies. At the same time, facilitated the communication among design team, business stakeholders, 
      global partners and headquarters.}
    \resumeItemListEnd

    \resumeSubheading
      {Sumitomo Heavy Industries,Ltd.}{Tokyo, Japan}
      {Research Engineer}{Apr 2013 - Sep 2018}
      \resumeItemListStart
        \resumeItem{Development of next generation 2K Gifford-McMahon cryocooler}
        {Carried out detailed analysis of previous cryocooler products and designed key components (regenerator etc.) of a highly compact Gifford-McMahon cryocoolers
        which can achieve 2K on second stage. Based on this work, published 2 papers in international cryogenic conference and 1 journal paper in Japan. 
        The design result is recognized as the most compact 2K Gifford-McMahon cryocooler in the world.
        This project was supported by the National Institute of Information 
        and Communications Technology (NICT), JAPAN.}
        \resumeItem{Development of next generation high capacity Gifford-McMahon cryocooler}
        {Carried out conceptual design and detail analysis of a next generation high capacity Gifford-McMahon cryocooler. Built test facilities to assist the
        prototyping of innovative design concepts. Published 2 papers in internation cryogenic conference based on this work.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

  
%-----------PROJECTS-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Mechnical design}
      {General knowledge of mechanical system, manufacturing process and design process. Can operate FEM analysis by Ansys Mechanical
      to facilitate and accelerate product prototyping. 3+ years experience of Solidworks. CSWA certificated by Solidworks.}
    \resumeSubItem{Thermal/Fluid dynamic analysis}
      {Built numerical tools to assist product design (Python, Fortran, D3.js). Carried out thermal/fluid dynamic analysis of complex 
      heat exchanger by OpenFoam.}
    \resumeSubItem{Programming}
      {Broad and in-depth knowledge of programming languages and general computer science as a mechanical engineer. Wrote numerical
      tools in C, Fortran, Python and Javascript. Built customized data acquisition software to assist in-house performance experiment.}
    \resumeSubItem{6-sigma (toolset of process immprovement)}
      {General understanding of the 6-$\sigma$ toolset and process. 3+ years working as a member and now project leader leading the team
      going through the design review process of a new product.}
\resumeSubHeadingListEnd


%----------Language skill-------
\section{Language Skills}
\resumeSubHeadingListStart
  \resumeSubItem{Mandarin Chinese}{Mother tongue}
  \resumeSubItem{English}{Professional efficiency; TOEFL iBT 108/120; GRE V156 + Q170}
  \resumeSubItem{Japanese}{Professional efficiency; JLPT N1 176/180}
  \resumeSubItem{German}{Intermediate efficiency; CEFR B1}
\resumeSubHeadingListEnd


%----------Publications-------
\section{Publication}
1.Experimental Investigation of Compact 2 K GM Cryocoolers, Physics Procedia, Volume 67, Pages 428-433, ISSN 1875-3892,
https://doi.org/10.1016/j.phpro.2015.06.053., (25th International Cryogenic Engineering Conference and the International Cryogenic Materials Conference in 2014, ICEC 25–ICMC 2014, Netherland)

2.Development of a compact 2K GM cryocooler, Cryogenic engineering, Vol.50 (2015) No.3 p. 125-131

3.Recent development status of compact 2 K GM cryocoolers,
IOP Conference Series: Materials Science and Engineering,
volume 101,
p.012136.
(Cryogenic Engineering Conference ,CEC 2015: Tucson, AZ, USA, June 28 - July 2, 2015)

4.Development status of a high cooling capacity single stage GM cryocooler,
Cryocooler 19,
pp. 291-297,
(International Conference of cryocoolers ,ICC19: San Diego, CA, USA, June 20-23, 2016)

5.Development of a pneumatic GM cryocooler with dual-displacer (Oral presentation, International workshop on cooling of HTS-Applications, IWC-HTS, Karlsruhe, Germany, September 13-15, 2017)

%----------Patent-------------


\end{document}
